Constraining the High Density Nuclear Symmetry Energy with Pions

### 2019-08-07 Documentation/PionMultiplicityAnalysis.tex
Adding better tables and gas section. Macros folder added

\subsection{Efficiency Corrected Spectra}

@@

 This is done for each momentum bin, which is assigned a total angular coverage of $\Omega_p$, for each momentum value, $p$. It is a good assumption that in the COM system the $\pi$ distribution is nearly isotropic. Correcting for the areas of the solid angle coverage we correct the counts in each momentum bin, $N_p$, by ${4\pi/\Omega_p}$, since this is the inverse of the fraction of space we measure in the TPC.

 \subsection{Solid Angle and Efficiency Corrected Spectra}

@@

\subsection{Correction for $A_{part}$ Effect on $M(\pi)$}

\begin{adjustbox}{max width=\linewidth,center}
\centering
\subfigure[With $A_{part}$ correction]{\includegraphics[width=0.5\textwidth]{multiplicitypion.png}}%
\subfigure[No correction]{\includegraphics[width=0.5\textwidth]{multiplicitypion_scaled.png}}%
\end{adjustbox}
\caption{Pion multiplicity before and after correction, compared with FOPI data.}
\label{fig:mult}

>>>>

  \subsection{Efficiency Correction}
The efficiency is corrected only for bins of $\theta$ and not bins in $\phi$ to improve statistics. The efficiency function is calculated only for the angular data cut region shown later. The zero count region is not corrected for and will be corrected by doing a solid angle correction later. Figure~\ref{fig:eff} shows the "effective`` efficiency for the pion vs momentum. Effective means we just take the efficiency corrected spectra and divide by the non-efficiency corrected spectra. The efficiency itself depends on  three parameters ($p$,$\theta$,$\phi$) and we are reducing it down to one parameter plot vs $p$.

\begin{figure}
\includegraphics[width=\textwidth]{effEff.png}
 \caption{Effective efficiency for pions}
 \label{fig:eff}
\end{figure}

@@

 This is done for each momentum bin, which is assigned a total angular coverage of $\Omega_p$, for each momentum value, $p$. It is a good assumption that in the COM system the $\pi$ distribution is nearly isotropic. Correcting for the areas of the solid angle coverage we correct the counts in each momentum bin, $N_p$, by ${4\pi/\Omega_p}$, since this is the inverse of the fraction of space we measure in the TPC. Figure~\ref{fig:solid} shows this $d\Omega$ made for each momentum bin, as a fraction of $4\pi$.

\begin{figure}[!hbt]
\includegraphics[width=\textwidth]{omega.png}
 \caption{Solid angle correction for each momentum bin.}
 \label{fig:solid}
\end{figure}

 \subsection{Efficiency Corrected and Solid Angle Corrected Spectra}
 Figure~\ref{fig:spectra} shows the efficiency corrected, and solid angle corrected, spectra. The efficiency corrected pion multiplicities are $\pi^- = .63$ and $\pi^+ = .12$ and the uncorrected multiplicities are $\pi^- = .63$ and $\pi^+ = .12$

\begin{figure}[!hbt]
\includegraphics[width=\textwidth]{spectra.png}
\caption{Efficiency and solid angle corrected spectra.}
\label{fig:spectra}
\end{figure}

@@

\subsection{Correction for $A_{part}$ Effect on $M(\pi)$}
In \cite{fopi}, there is a small correction for the dependence of the multiplicity on the number of participants. I will leave it to the reader to read the paper. The function used to correct is given in Eq.~\ref{eq:corr}, where $\tau = .86$, the correction factor being, $f=1.05$. We must scale our answer by this estimate to get compare with the  ${}^{197}$Au + ${}^{197}$Au FOPI data. The only issue here is this scaling law is not for the beam energy we are at. This is for 1 AGeV but roughly speaking it should not depend so much on beam energy.

\begin{equation}
f = \frac{256}{394 *.9}^{\tau -1}
\label{eq:corr}
\end{equation}

Figure~\ref{fig:mult} shows the corrected (and uncorrected) pion multiplicity, as calculated from Table~\ref{tb:apart} and Table~\ref{tb:pionmult}, plotted against the FOPI data. The blue dotted curve is the fit from the published data, and the red line fit is with our new point added in. The trend is in good agreement with our measured data. The error bar on the scaled multiplicity is coming from the error bar in $A_{part}$ from the uncertainty in the range in impact parameters probed.

\begin{figure}[!hbt]
\begin{adjustbox}{max width=\linewidth,center}
\centering
\subfigure[With $A_{part}$ correction]{\includegraphics[width=0.5\textwidth]{multiplicitypion.png}}%
\subfigure[No correction]{\includegraphics[width=0.5\textwidth]{multiplicitypion_scaled.png}}%
\end{adjustbox}
\caption{Pion multiplicity before and after correction, compared with FOPI data.}
\label{fig:mult}

### 2019-08-07 chapters/ch_data_analysis.tex
Adding better tables and gas section. Macros folder added

\section{Calibrations}

\paragraph{Electronics calibration}

\paragraph{Anode gain calibration}

\section{Corrections}
\paragraph{Extending the dynamic range of Electronics}

@@

\section{Drift Task}
The drift task takes the energy loss points calculated from Geant4 and converts them into electrons.  and then modeling their drift behavior in the field cage. As discussed previously the various processes[CITE To formula about drifting electronc]

@@

\section{Pad Response Task}
After the avalanche process of the previous task, the total charge of the event is split over several pads defined by the Pad Response Function (as discussed in section ????). As shown in Fig.~\ref{fig:onepad}, there are three wires that lie directly above a given pad. The $z$ coordinate of the avalanche can only be one of these three wires, where as the $x$ coordinate can be any value along the wire. The functional form of the software PRF (given in Eq.~\ref{eq:softPRF}), was tuned to match the experimental data. Shown in Fig.~\ref{fig:mcdataPRF}, we see the tuned software PRF can match the experimental PRF from data over several crossing angles (as mentioned in Chapter ???? governs the shape of the PRF).

@@

\section{Electronics Task}
The electronics task takes the total charge on each pad and simulates the electronics response, converting electronics into ADC channels. Accounting for the pedestal, the measured output in ADC channels (for a given gain setting) is given in Eq.~\ref{eq:etoADC}.

@@

\section{Track Embedding}
Track embedding is the process of taking a simulated MC track from Geant4 and embedding its response into a real data event. After reconstructing this new embedded event we match the input MC track embedded to its corresponding final reconstructed track.  By doing so we can evaluate the response of the entire TPC system to any given input value. The TPC system is composed of three major components (each which can introduce errors and or biases) the software, the detector, and the experimental setup.

@@

\section{Efficiency Corrections}
Since the \spirit TPC is a fixed target experiment it's angular coverage is certainly not 4$\pi$. Because the target is several cm away from the widow of the field cage the geometric acceptance is not even 2$\pi$. The rectangular design complicates the calculation of the geometric acceptance, or the efficiency.

>>>>

\section{Calibrations and Corrections}
Cocktail Calibration

\subsection{Electronics calibration}
Pulse the ground grid. 
Picture of calibration of channels before and after.

\subsection{Anode gain calibration}
Picture of low vs high gain channels and fit

\subsection{Extending the dynamic range of the Electronics}
Add paper here.

\subsection{Space Charge Corrections}
Overview
Discuss the relevant time scales, drift lengths, magnitudes, and locations of space charge
Figure of cartoon sheet charge
Figure of beam path locations for different beam types
Table of energy loss tables for energies and beam types
Reference appendix for poisson solver 
Tables for ion drift velocity in P-10 Gas reference Sauli
Figure of sDAC or POCA 
Figure of cartoon of what is happening to tracks
Figure of correction map in TPC and MC map 
Figure of before and after correction BDC vs reco momentum
Figure of track residuals before and after?

In theory, a TPC functions with the electric and magnetic fields parallel to each other. In this way the electrons move opposite to the electric field winding tightly around the magnetic field lines, reducing transverse diffusion in the process. In practice, due to the finite size of the dipole magnet and field cage, there are traverse components to both the electric and magnetic fields. These transverse components introduce drift velocities in the transverse directions, causing a shift in the measured cluster positions of the track. Thereby introducing systematic shifts in the calculation of the momentum and the vertex calculation.

Most of the time the beam does not undergo a nuclear collision with the target and passes through the TPC drift volume. The KATANA array threshold was set to veto such events, ensuring the gating grid remain closed to prevent the large amount of charge deposited by the beam into the avalanche region. While the electron drift velocity is fast enough for the electrons produced by the unreacted beam to terminate on the closed gating grid, the drift velocities of the positive ions produced are of order $10^{-4}$ times slower. At higher beam rates the positive charge is allowed to pile up producing a region of positive space charge, introducing perturbations to the nominal electric field.

Since the beam comes in along the z-axis, and the drift direction of the ions is in the -y direction, we can estimate the charge density as an uniform sheet charge. The surface charge density is related to the beam rate, ion drift length, ion drift velocity, and the energy loss of the beam. Though the incoming beam comes randomly, the slow drift velocity combined with the high beam rate makes the uniform approximation valid. Tracking or estimating the beam rate as a function of time with in a given run would provide a better estimate of the space charge. Or experimentally a laser system could be pulsed after each event (throughout the drift volume), giving the experimental correction map for the drift. While the potential for a laser system was implemented in the field cage design, a laser system ultimately was not developed for the \spirit tpc.

The beam rate within a run is roughly constant, therefore we can estimate the space charge and provide a first order correction for the space charge effect.

As mentioned in CHAPTER ???, the cocktail beam momentum was well known to within 1\% as set by the BIGRips spectrometer. Also time of flight analysis of upstream and downstream scintilators also independently confirmed the beam rigidity setting. The expected momentum is given in TABLE ??? as calculated by from the beam rigidity setting of the magnet (WHICH MAGNET). The measured momenta as determined by the TPC software (given in FIG TABLE ), shows a disagreement on the level of 5\% too high. We noticed that if one only uses the first 90 layers (out of 112) of the TPC, the momenta is lower; one should expect the momentum to go higher as the track length is shorter (short tracks effectively are straight lines). 
In the cocktail beam there is no un-reacted beam causing any significant space charge. The magnetic field map of the SAMURAI magnet has been calculated by TOSCA simulation CITE ???, and several points have been verified experimentally with a hall probe to be within XXX \%. We assume that the electric field (to first order) is uniform in the y-direction. Using Garfield++ CITE ???, we can model the transverse drift of the electrons in the presence of such fields.

A grid of electrons uniformly distributed in the TPC model space were drifted to the gating grid position. The final shifts in the x and z positions was measured.

@@

\subsection{Drift Task}
The drift task takes the energy loss points calculated from Geant4 and converts them into electrons.  and then modeling their drift behavior in the field cage. As discussed previously the various processes[CITE To formula about drifting electronc]

@@

\subsection{Pad Response Task}
After the avalanche process of the previous task, the total charge of the event is split over several pads defined by the Pad Response Function (as discussed in section ????). As shown in Fig.~\ref{fig:onepad}, there are three wires that lie directly above a given pad. The $z$ coordinate of the avalanche can only be one of these three wires, where as the $x$ coordinate can be any value along the wire. The functional form of the software PRF (given in Eq.~\ref{eq:softPRF}), was tuned to match the experimental data. Shown in Fig.~\ref{fig:mcdataPRF}, we see the tuned software PRF can match the experimental PRF from data over several crossing angles (as mentioned in Chapter ???? governs the shape of the PRF).

@@

\subsection{Electronics Task}
The electronics task takes the total charge on each pad and simulates the electronics response, converting electronics into ADC channels. Accounting for the pedestal, the measured output in ADC channels (for a given gain setting) is given in Eq.~\ref{eq:etoADC}.

@@

\subsection{Simulating Saturation}
Add figure showing saturated time bucket spectra with location of saturation identified and with pulse shape from embedding I would like to add and how it blocks it.
Add Figure with 2D pad plane response with and without saturation flag

\section{Monte Carlo Track Embedding}
Add Figure of MC track embedding

Track embedding is the process of taking a simulated MC track from Geant4 and embedding its response into a real data event. After reconstructing this new embedded event we match the input MC track embedded to its corresponding final reconstructed track.  By doing so we can evaluate the response of the entire TPC system to any given input value. The TPC system is composed of three major components (each which can introduce errors and or biases) the software, the detector, and the experimental setup.

@@

\subsection{MC and Data Comparison}
Add Figure of Pad response function for pion,proton.... for MC vs Data vs angles...
Add Figure of Number of clusters of MC vs Data
Add Figure of dEdx MC vs Data
Add Figure of Momentum resolution MC vs Data
Add Figure of track residuals? MC vs data?

\section{Efficiency Corrections}
Add Figures of efficiency vs angles in TPC polar angle plot for pions

Since the \spirit TPC is a fixed target experiment it's angular coverage is certainly not 4$\pi$. Because the target is several cm away from the widow of the field cage the geometric acceptance is not even 2$\pi$. The rectangular design complicates the calculation of the geometric acceptance, or the efficiency.

\section{Beam Particle Identification}
Figures of beam contaminants in our beam PID line. 
Table of beam purity reference to Jon's thesis paper

\section{Solid angle coverage}

### 2019-08-07 chapters/ch_experiment.tex
Adding better tables and gas section. Macros folder added

\section{S$\pi$RIT TPC Overview}
The Samurai Pion-Reconstruction and Ion Tracker Time Projection Chamber (S$\pi$RI TPC) is a Multi-Wire Proportional Counter developed to measure pions and other light charge particles resulting from radioactive heavy ion collisions in a fixed target experiments.  The TPC is enclosed in a thin aluminum sheet walls all around in order to minimize neutron scattering and to allow for light charged particles to reach the arrays of scintillating bars detectors on the sides and downstream of the TPC. The S$\pi$RI TPC was developed to fit inside the Samurai dipole magnet used at the Rare Isotope Beam Factory (RIBF) at RIKEN in Wako-shi, Japan \cite{riken}; the dipole gap limited the vertical space of the TPC. More detail and specifications of the Samurai dipole magnet are given in \cite{samurai}.

A target ladder allowed for up to 5 fixed targets to be mounted. A ACME worm gear allowed for the x-axis motion for changing the targets. The motion of this worm gear was translated through the target motion feed-through by several brass gears and non-magnetic gear boxes. The motion of the target ladder could be controlled by hand or by operation of the drill. The targets were mounted on stand-offs on the target ladder and also had z-axis motion. This allowed for the targets to be positioned as close as possible to the thin window of the field cage, maximizing the geometric acceptance.

The electronics were mounted to the aluminum top plate. Several aluminum ribs were mounted to the top of the plate to bring structural rigidity. Because of this the top plate flatness was within 150$\mu$m across the whole top plate as measured by a laser position system. The charge sensitive pads of the pad plane were etched into several circuit boards were recessed and glued to the bottom portion of the top plate. Vias through the pad plane circuit boards brought the signal traces from the pads to surface mount pads on the other side of the boards. Several holes cut through the top plate allowed for the interface cables of the electronics to be connected to these surface pads.

@@

@@

\section{Considerations when constructing a TPC}
Several considerations went into the construction of the S$\pi$RI TPC which I wish to summarize and document here. All materials and glue of the TPC were selected as low out-gassing materials. Several materials that are common place in nuclear labs, from vacuum grease to o-rings, out-gas organic chemicals into the counter gas which damage the TPC by permanently lowering the gain over time. The organic molecules responsible are difficult to identify exactly, but lists of good and bad materials are well known in the literature from experiments. If a material we wished to used was not on these lists we placed the material in a clean chamber with the counter gas and flowed this counter gas through a small proportional counter making sure the gain did not drop at high collection rates when exposed to a high rate alpha Americium source.

\section{Field Cage}

@@

The field cage was constructed from several panels of printed circuit boards (PCBs). The epoxy in the common PCB substrate FR4 contains bromine which is not suitable for the long term operation of a TPC, as the bromine will eventually cause gain reduction of the wires [CITE]. The halogen free material chosen was Rodgers ????. We build the TPC with the option to run explosive gases such  hydrogen, thus we decided to have field cage an isolated volume from the rest of the TPC enclosure. While the risk of a high voltage spark was minimized using the voltage step down, the risk of sparking when using an explosive gas could be further minimized by isolating the detector volume from the enclosure volume thereby allowing you to run an insulating gas between the field cage while running the explosive gas inside the detector volume only.

@@

\section{Voltage Step Down}

@@

\section{Wire Planes}

\section{Pad Plane}

\section{Electronics}

@@

\begin{table}
 \begin{tabular}{||c c c c||} 
 \hline
 \multicolumn{4}{|c|}{GET Electronics Settings} \\
 \hline
 GET settings & All options & ${}^{132}$Sn + ${}^{124}$Sn & ${}^{124}$Sn + ${}^{112}$Sn \\
 \hline
 ADC bit range      & 14 bits &  &  \\
 \hline
 Sampling frequency & 1 - 100 MHz &   &    \\
 \hline
 Dynamic range      & .12,.24,1.0,10 pC & & \\
 \hline
 Peaking time       &  69,117,232,501,720, 1014 ns &  &   \\
 \hline
 Time bucket        & 512 & 270 & 270  \\
 \hline
\end{tabular}
\caption{Summary of the optional settings of the GET electronics and those used during the 20?????? experimental runs}
\label{tb:spiritoverview}
\end{table}

\section{S$\pi$RIT at RIBF}

\section{Kyoto Multiplicity Trigger}
\section{Krakow ?????? (KATANA)}
\section{Ancillary Detectors }
\section{Radio Isotope Beam Factory (RIBF) Facility }

@@

\section{Experimental setup}
\section{Trigger Condition}

>>>>

\section{S$\pi$RIT TPC Overview}
Add Overview image with labels

The Samurai Pion-Reconstruction and Ion Tracker Time Projection Chamber (S$\pi$RI TPC) is a Multi-Wire Proportional Counter developed to measure pions and other light charge particles resulting from radioactive heavy ion collisions in a fixed target experiments.  The TPC is enclosed in a thin aluminum sheet walls all around in order to minimize neutron scattering and to allow for light charged particles to reach the arrays of scintillating bars detectors on the sides and downstream of the TPC. The S$\pi$RI TPC was developed to fit inside the Samurai dipole magnet used at the Rare Isotope Beam Factory (RIBF) at RIKEN in Wako-shi, Japan \cite{riken}; the dipole gap limited the vertical space of the TPC. More detail and specifications of the Samurai dipole magnet are given in \cite{samurai}.

A target ladder allowed for up to 5 fixed targets to be mounted. A ACME worm gear allowed for the x-axis motion for changing the targets during the experiment, without needing to open or move the TPC. The motion of this worm gear was translated through the target motion feed-through by several brass gears and non-magnetic gear boxes. The motion of the target ladder could be controlled by hand or by operation of the drill. The targets were mounted on stand-offs on the target ladder and also had z-axis motion. This allowed for the targets to be positioned as close as possible to the thin window of the field cage, maximizing the geometric acceptance.

The electronics were mounted to the aluminum top plate. Several aluminum ribs were mounted to the top of the plate to bring structural rigidity. A flatness within 150$\mu$m was achieved across the whole top plate as measured by a laser position system. The charge sensitive pads of the pad plane were etched into several circuit boards were recessed and glued to the bottom portion of the top plate. Vias through the pad plane circuit boards brought the signal traces from the pads to surface mount pads on the other side of the boards. Several holes cut through the top plate allowed for the interface cables of the electronics to be connected to these surface pads.

@@

\begin{table*}\centering
\ra{1.3}
\begin{tabular}{@{}rr@{}}\toprule 
\multicolumn{2}{c}{\spirit TPC Overview} \\
 \midrule
Pad plane area & 1.3 m x .9 m\\
Pad size       & 1.2 cm x .8 cm \\
Number of pads & 12096 (112 x 108) \\
Gas composition& 90\% Ar + 10\% CH${}_4$  \\
Multiplicity limit & 200  \\
dE/dx range        & Z=1-8, $\pi$, p,d,t,He,Li-O \\
Drift length       & 50 cm \\
\bottomrule
\end{tabular}
\caption{Caption}
\end{table*}

@@

\subsection{Enclosure}

\subsection{Voltage Step Down}

\subsection{Field Cage}

@@

The field cage was constructed from several panels of printed circuit boards (PCBs). The epoxy in the common PCB substrate FR4 contains bromine which is not suitable for the long term operation of a TPC, as the bromine will eventually cause gain reduction of the wires [CITE]. The halogen free material chosen was Rodgers ????. We built the TPC with the option to run explosive gases such  hydrogen, thus we decided to have field cage an isolated volume from the rest of the TPC enclosure. While the risk of a high voltage spark was minimized using the voltage step down, the risk of sparking when using an explosive gas could be further minimized by isolating the detector volume from the enclosure volume thereby allowing you to run an insulating gas between the field cage while running the explosive gas inside the detector volume only.

@@

\subsection{Voltage Step Down}

@@

\subsection{Wire Planes}
Add figure of gating grid transparency closed and open configuration

\subsection{Pad Plane}
Add figure of close up of pad plane

\subsection{Electronics}

@@

\begin{table}
 \begin{tabular}{||c c c c||} 
 \hline
 \multicolumn{4}{|c|}{GET Electronics Settings} \\
 \hline
 GET settings & All options & ${}^{132}$Sn + ${}^{124}$Sn & ${}^{124}$Sn + ${}^{112}$Sn \\
 \hline
 ADC bit range      & 14 bits &  &  \\
 \hline
 Sampling frequency & 1 - 100 MHz &   &    \\
 \hline
 Dynamic range      & .12,.24,1.0,10 pC & & \\
 \hline
 Peaking time       &  69,117,232,501,720, 1014 ns &  &   \\
 \hline
 Time bucket        & 512 & 270 & 270  \\
 \hline
\end{tabular}
\caption{Summary of the optional settings of the GET electronics and those used during the 20?????? experimental runs}
\label{tb:getoverview}
\end{table}

\subsection{Considerations when constructing a TPC}
Several considerations went into the construction of the S$\pi$RI TPC which I wish to summarize and document here. All materials and glues of the TPC were selected as low out-gassing materials. Several materials (that are common place in nuclear labs), such as vacuum grease, viton o-rings, all out-gas organic chemicals into the counter gas which damage the TPC by permanently lowering the gain over time. The organic molecules responsible are difficult to identify exactly, but lists of good and bad materials are well known in the literature from experiments. If a material we wished to used was not on these lists we placed the material in a clean chamber with the counter gas and flowed this counter gas through a small proportional counter making sure the gain did not drop at high collection rates when exposed to a high rate alpha Americium source.

\subsection{Gas Properties}

\begin{figure}[H]
\includegraphics[width=\linewidth]{driftvel.png}
\caption{Drift velocity of electrons in P10 gas.}
\label{fig:driftvel}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{gain.png}
\caption{Number of electrons produced in a single avalanche on an anode wire. Two different voltages were simulated using Garfield++ at 1470 $V$ and 1214 $V$. The expected Polya distribution fit is also given in yellow.}
\label{fig:anodegain}
\end{figure}

\begin{table}[!htp] % not just 'h!'
\centering % not a center environment
\begin{tabular}{
  @{}
  l
  S[table-format=1.2]
  S[table-format=1.2]
  S[table-format=1.2]
  S[table-format=5.2]
  S[table-format=5.2]
  @{}
}
\toprule
Gas properties &
 {$\sigma_{t}$} &
 {$\sigma_{l}$} &
 {$v_{d}$} &
 {$G_{h}$} &
 {$G_{l}$} \\
&
  {($\si{\centi\meter}^{-1/2}$)} &
  {($\si{\centi\meter}^{-1/2}$)} &
  {(\si{\centi\meter\per\micro\second})} \\
\midrule
\phantom{abc}   &.024   &.034  &5.43   &  903   &150     \\
\bottomrule
\end{tabular}

\caption{}
\label{tb:gasprop}
\end{table}

Add table for gas diffusion

\section{Ancillary Detectors }
\subsection{Kyoto Multiplicity Trigger}
\subsection{Krakow ?????? (KATANA)}

\section{Radio Isotope Beam Factory (RIBF) Facility }
Cyclotron facility overview.
Samurai line overview.
Beam line element overview.
Big rips beam PID. reference

\section{S$\pi$RIT at RIBF}
Picture of setup.

@@

\section{Experimental Setup}

\section{Trigger Condition}
How it was made using kyoto krakow

\section{Collision Data Taken}

### 2019-08-07 chapters/ch_intro.tex
Adding better tables and gas section. Macros folder added

\chapter{Introduction}
\section{From Nuclear Forces to the Equation of State}
\section{Phases of Nuclear Matter}
\section{The Nuclear Equation of State}
\section{Previous Constraints}
\section{Motivation for building the S$\pi$RIT TPC}

>>>>

\chapter{Introduction}

\section{From Nuclear Forces to the Equation of State}
Figure showing the nuclear forces for the pp, pn, nn 
Figure showing the binding energy vs p-n asym

\section{Phases of Nuclear Matter}

\section{The Nuclear Equation of State}

\section{Boltzmann Ulong Uhlenbeck (BUU) Transport Code}
Figure of transport simulation code showing collision progression

\section{Observables}
Figure showing p-n observable lessens at high energy and from all densities

\section{The $\pi$ observable}
Figure showing delta resonance 
Figure showing pion's produced at 2po 
Figure showing fermi motion effect

\section{Previous Constraints}
Figure showing GW constraint and other previous constraints 
Can you group all the constraints to one nice plot???

\section{Motivation for building the S$\pi$RIT TPC}

### 2019-08-07 chapters/ch_results.tex
Adding better tables and gas section. Macros folder added

\chapter{Results}
\section{Comparison to Theory}
\section{$\pi$ Yields}
\section{$\pi^-$/$\pi^+$ Ratio}
\section{Constraint on the Symmetry Energy}

>>>>

\chapter{Results}
\section{Comparison to Theory}
Add figure of Pion spectra for different theory 
Reference paper for multiple theories

\section{$\pi$ Yields}
Add figure on Glauber model 
Add figure on comparison to FOPI data
Add figure of angular coverage of TPC spectra

\section{$\pi^-$/$\pi^+$ Ratio}
Add figure of Theory for pion ratios

\section{Pion Inferometry}

\section{Constraint on the Symmetry Energy}
maybe not...
